CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability

### 2018-11-04 gpus/paper.tex
some abstract

\newcommand{\castro}{{\sf Castro}}

@@

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
blah
\end{abstract}

@@

>>>>

\newcommand{\castro}{{\sf Castro}}
\newcommand{\maestro}{{\sf Maestro}}

@@

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
We describe a performance portable version of the \castro\ hydrodynamics
code that is able to achieve excellent scaling on both CPU and GPU-based
supercomputers.
\end{abstract}

@@

\subsection{Pure hydrodynamics}

\subsection{Reaction test}

\subsection{X-ray burst}

This problem uses constant gravity, so all of the physics can be done on the GPUs.

\section{Summary}

Future work: gravity on GPUs (multigrid or multipole), port of \maestro\ following
the same ideas.
